---
title: "Explore 1999-2016 Harvest Data"
always_allow_html: yes
output:
  html_document:
    df_print: paged
    fig_height: 8
    fig_width: 11
  pdf_document: default
---

```{r setup, include = FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
#knitr::opts_knit$set(root.dir = "C:/Dev/Projects/CafPlantGridPointSurvey/R/AggregateYieldAndBiomass_1999-2016")

library(tidyverse)
library(plotly)
library(sf)
library(tmap)
```

```{r}
source("../src/functions.R")
source("../src/cleaningFunctions.R")
```

```{r, include=FALSE}
setwd("../")
df <- get_clean1999_2016(rm.outliers = F)
sf <- st_as_sf(df, coords = c("Longitude", "Latitude"), crs = 4326)

df.dirty <- get_dirty1999_2009() %>% 
  filter(!is.na(ID2), `Crop...3` != "Fallow") %>% 
  replace(. == "winter wheat", "WW") %>%
  replace(. == "spring wheat", "SW") %>%
  replace(. == "spring barley", "SB") %>%
  replace(. == "spring canola", "SC") %>%
  replace(. == "spring pea", "SP") %>%
  replace(. == "winter barley", "WB") %>%
  replace(. == "winter pea", "WP") %>%
  replace(. == "winter canola", "WC") %>%
  replace(. == "Winter Canola", "WC") %>%
  replace(. == "winter lentil", "WL") %>%
  replace(. == "Garbonzo Beans", "GB")

sf.dirty <- df.dirty %>% 
  filter(!is.na(X) & !is.na(Y)) %>% 
  st_as_sf(coords = c("X", "Y"), crs = 4326)

boundary <- st_read("input/CookEastBoundary_20180131.geojson")
```

# Quality Review of Grain Nitrogen (%) and Grain Carbon (%)

## Maps of grain N from different sources for HY1999 - HY2009

* GrainNUbbie = Data from Ubbie's file with 0 values set to NULL
* GrainNUnger = Data from Unger's file with 0 values set to NULL and Excel copy/paste errors set to NULL
* GrainNFinal = Data after removing extreme outliers from GrainNUbbie and GrainNUnger then averaging if both have values and taking only present if single value

```{r}

columns <- c("GrainNUbbie", "GrainNUnger", "GrainNFinal")
years <- seq(1999, 2009, 1)

for(y in years) {
  for(c in columns) {
    print(sf.dirty %>% 
      filter(Year == y) %>% 
      getMapQuartileOutliers(c, "Year", "Crop", boundary, "ID2") +
      tm_layout(title = paste("HY ", y, ": ", c, sep = "")) +
      tm_grid(alpha = 0.25, labels.inside.frame = F) +
      tm_compass())
  }
}

```

## Maps of grain C from different sources for HY1999 - HY2009

* GrainCUbbie = Data from Ubbie's file with 0 values set to NULL
* GrainCUnger = Data from Unger's file with 0 values set to NULL and Excel copy/paste errors set to NULL
* GrainCFinal = Data after removing extreme outliers from GrainCUbbie and GrainCUnger then averaging if both have values and taking only present if single value

```{r}

columns <- c("GrainCUbbie", "GrainCUnger", "GrainCFinal")
years <- seq(1999, 2009, 1)

for(y in years) {
  for(c in columns) {
    print(sf.dirty %>% 
      filter(Year == y) %>% 
      getMapQuartileOutliers(c, "Year", "Crop", boundary, "ID2") +
      tm_layout(title = paste("HY ", y, ": ", c, sep = "")) +
      tm_grid(alpha = 0.25, labels.inside.frame = F) +
      tm_compass())
  }
}

```

## Maps of grain N for HY2010 - HY2016
```{r}

columns <- c("GrainNitrogen")
years <- seq(2010, 2016, 1)

for(y in years) {
  for(c in columns) {
    print(sf %>% 
      filter(HarvestYear == y) %>% 
      getMapQuartileOutliers(c, "HarvestYear", "Crop", boundary, "ID2") +
      tm_layout(title = paste("HY ", y, ": ", c, sep = "")) +
      tm_grid(alpha = 0.25, labels.inside.frame = F) +
      tm_compass())
  }
}

```

## Maps of grain C for HY2010 - HY2016
```{r}

columns <- c("GrainCarbon")
years <- seq(2010, 2016, 1)

for(y in years) {
  for(c in columns) {
    print(sf %>% 
      filter(HarvestYear == y) %>% 
      getMapQuartileOutliers(c, "HarvestYear", "Crop", boundary, "ID2") +
      tm_layout(title = paste("HY ", y, ": ", c, sep = "")) +
      tm_grid(alpha = 0.25, labels.inside.frame = F) +
      tm_compass())
  }
}

```