---
title: "Explore 1999-2016 Harvest Data"
always_allow_html: yes
output:
  html_document:
    df_print: paged
    fig_height: 8
    fig_width: 11
  pdf_document: default
---

```{r setup, include = FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
#knitr::opts_knit$set(root.dir = "C:/Dev/Projects/CafPlantGridPointSurvey/R/AggregateYieldAndBiomass_1999-2016")

library(tidyverse)
library(plotly)
library(sf)
library(tmap)
```

```{r}
source("../src/functions.R")
source("../src/cleaningFunctions.R")
```

```{r, include=FALSE}
setwd("../")
df <- get_clean1999_2016(rm.outliers = F)
sf <- st_as_sf(df, coords = c("Longitude", "Latitude"), crs = 4326)

df.dirty <- get_dirty1999_2009() %>% 
  filter(!is.na(ID2), `Crop...3` != "Fallow") %>% 
  replace(. == "winter wheat", "WW") %>%
  replace(. == "spring wheat", "SW") %>%
  replace(. == "spring barley", "SB") %>%
  replace(. == "spring canola", "SC") %>%
  replace(. == "spring pea", "SP") %>%
  replace(. == "winter barley", "WB") %>%
  replace(. == "winter pea", "WP") %>%
  replace(. == "winter canola", "WC") %>%
  replace(. == "Winter Canola", "WC") %>%
  replace(. == "winter lentil", "WL") %>%
  replace(. == "Garbonzo Beans", "GB")

sf.dirty <- df.dirty %>% 
  filter(!is.na(X) & !is.na(Y)) %>% 
  st_as_sf(coords = c("X", "Y"), crs = 4326)

boundary <- st_read("input/CookEastBoundary_20180131.geojson")
```

# Maps by year and crop
```{r, fig.width=11, fig.asp=1, out.width="100%"}
tmap_mode("plot")
sf %>% 
  filter(!is.na(GrainYieldDryPerArea)) %>% 
  tm_shape() +
  tm_dots(size = 0.1, col = "Crop", palette = "Set1") +
  tm_facets(by="HarvestYear")
```

# Quality review of crop type

## Maps of years where Ubbie's data did not match Unger's data

* Dots on map are colored based on Unger's data
* Locations that differ are squares and have a label that corresponds to Ubbie's designation

```{r, fig.width=11, fig.asp=1, out.width="100%"}
cropError <- sf.dirty %>% 
  filter(Year %in% c(2001, 2003, 2007, 2008)) %>% 
  mutate(CropLabelError = (`Crop...3` != Crop)) %>% 
  select(Year, ID2, `Crop...3`, Crop, CropLabelError) %>% 
  mutate(Label = case_when(CropLabelError == TRUE ~ paste(`Crop...3`, sep = ",")))

tm_shape(cropError) +
  tm_dots(col = "Crop", shape = "CropLabelError", size = 0.7) +
  tm_facets(by = "Year") +
  tm_text("Label", size = 0.8, ymod = 0.2)
```

# Quality Review of Grain Nitrogen (%) and Grain Carbon (%)

## Maps of grain N from different sources for HY1999 - HY2009

* GrainNUbbie = Data from Ubbie's file with 0 values set to NULL
* GrainNUnger = Data from Unger's file with 0 values set to NULL and Excel copy/paste errors set to NULL
* GrainNFinal = Data after removing extreme outliers from GrainNUbbie and GrainNUnger then averaging if both have values and taking only present if single value

```{r}

columns <- c("GrainNUbbie", "GrainNUnger", "GrainNFinal")
years <- seq(1999, 2009, 1)

for(y in years) {
  for(c in columns) {
    print(sf.dirty %>% 
      filter(Year == y) %>% 
      getMapQuartileOutliers(c, "Year", "Crop", boundary, "ID2") +
      tm_layout(title = paste("HY ", y, ": ", c, sep = "")) +
      tm_grid(alpha = 0.25, labels.inside.frame = F) +
      tm_compass())
  }
}

```

## Maps of grain C from different sources for HY1999 - HY2009

* GrainCUbbie = Data from Ubbie's file with 0 values set to NULL
* GrainCUnger = Data from Unger's file with 0 values set to NULL and Excel copy/paste errors set to NULL
* GrainCFinal = Data after removing extreme outliers from GrainCUbbie and GrainCUnger then averaging if both have values and taking only present if single value

```{r}

columns <- c("GrainCUbbie", "GrainCUnger", "GrainCFinal")
years <- seq(1999, 2009, 1)

for(y in years) {
  for(c in columns) {
    print(sf.dirty %>% 
      filter(Year == y) %>% 
      getMapQuartileOutliers(c, "Year", "Crop", boundary, "ID2") +
      tm_layout(title = paste("HY ", y, ": ", c, sep = "")) +
      tm_grid(alpha = 0.25, labels.inside.frame = F) +
      tm_compass())
  }
}

```

## Maps of grain N for HY2010 - HY2016
```{r}

columns <- c("GrainNitrogen")
years <- seq(2010, 2016, 1)

for(y in years) {
  for(c in columns) {
    print(sf %>% 
      filter(HarvestYear == y) %>% 
      getMapQuartileOutliers(c, "HarvestYear", "Crop", boundary, "ID2") +
      tm_layout(title = paste("HY ", y, ": ", c, sep = "")) +
      tm_grid(alpha = 0.25, labels.inside.frame = F) +
      tm_compass())
  }
}

```

## Maps of grain C for HY2010 - HY2016
```{r}

columns <- c("GrainCarbon")
years <- seq(2010, 2016, 1)

for(y in years) {
  for(c in columns) {
    print(sf %>% 
      filter(HarvestYear == y) %>% 
      getMapQuartileOutliers(c, "HarvestYear", "Crop", boundary, "ID2") +
      tm_layout(title = paste("HY ", y, ": ", c, sep = "")) +
      tm_grid(alpha = 0.25, labels.inside.frame = F) +
      tm_compass())
  }
}

```

# Summary by year and crop - Outliers not removed from these values

```{r}
p <- df %>% 
  filter(!is.na(GrainYieldDryPerArea)) %>% 
  ggplot(aes(x = as.factor(HarvestYear), y = GrainYieldDryPerArea), na.rm = TRUE) +
  geom_boxplot() +  
    facet_wrap(~ Crop) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "harvest year", y = "yield (g / m2)")
ggplotly(p)
#p
```

```{r}
p <- df %>% 
  filter(!is.na(ResidueMassDryPerArea)) %>% 
  ggplot(aes(x = as.factor(HarvestYear), y = ResidueMassDryPerArea), na.rm = TRUE) +
  geom_boxplot() +  
    facet_wrap(~ Crop) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "harvest year", y = "mean residue (g / m2)")
ggplotly(p)
#p
```

```{r}
p <- df %>% 
  filter(!is.na(ResidueMassDryPerArea) & !is.na(GrainYieldDryPerArea)) %>% 
  mutate(HarvestIndex = GrainYieldDryPerArea / (GrainYieldDryPerArea + ResidueMassDryPerArea)) %>% 
  ggplot(aes(x = as.factor(HarvestYear), y = HarvestIndex), na.rm = TRUE) +
  geom_boxplot() +  
    facet_wrap(~ Crop) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "harvest year", y = "harvest index")
ggplotly(p)
#p
```

```{r}
p <- df %>% 
  filter(!is.na(GrainCarbon)) %>% 
  ggplot(aes(x = as.factor(HarvestYear), y = GrainCarbon), na.rm = TRUE) +
  geom_boxplot() +  
    facet_wrap(~ Crop) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "harvest year", y = "grain carbon (%)")
ggplotly(p)
#p
```

```{r}
p <- df %>% 
  filter(!is.na(GrainNitrogen)) %>% 
  ggplot(aes(x = as.factor(HarvestYear), y = GrainNitrogen), na.rm = TRUE) +
  geom_boxplot() +  
    facet_wrap(~ Crop) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "harvest year", y = "grain nitrogen (%)")
ggplotly(p)
#p
```

```{r}
p <- df %>% 
  filter(!is.na(ResidueCarbon)) %>% 
  ggplot(aes(x = as.factor(HarvestYear), y = ResidueCarbon), na.rm = TRUE) +
  geom_boxplot() +  
    facet_wrap(~ Crop) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "harvest year", y = "residue carbon (%)")
ggplotly(p)
#p
```

```{r}
p <- df %>% 
  filter(!is.na(ResidueNitrogen)) %>% 
  ggplot(aes(x = as.factor(HarvestYear), y = ResidueNitrogen), na.rm = TRUE) +
  geom_boxplot() +  
    facet_wrap(~ Crop) +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "harvest year", y = "residue nitrogen (%)")
ggplotly(p)
#p
```